### 2020-01-12 CV/cv-sections/education.tex
cv update, site update

\cventry
{MS/PhD in Computer Science } % Degree
{King Abdullah University of Science and Technology} % Institution
{Thuwal, Saudi Arabia} % Location
{Sep. 2018 - PRESENT} % Date(s)
{
}
%------------------------------------------------

>>>>

\cventry
{PhD in Computer Science } % Degree
{King Abdullah University of Science and Technology} % Institution
{Thuwal, Saudi Arabia} % Location
{Jan. 2020 - PRESENT} % Date(s)
{
}

\cventry
{MS in Computer Science } % Degree
{King Abdullah University of Science and Technology} % Institution
{Thuwal, Saudi Arabia} % Location
{Sep. 2018 - Dec. 2019} % Date(s)
{
}
